# Paper results

# Results:  Intracranial volume

## All site results:  Intracranial volume

```{r,results = 'asis', echo = T}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
fit <- aov( total.volume ~ dx.group + site + age + fiq, data = results )
print( xtable( anova( fit ) ), type = "html" )
```

## Per site results:  Intracranial volume

`total.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
  age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
  {
  if( count < 8 )
    {
    resultsPerSite <- results[which( results$site == site ),]
    fit <- anova( aov( total.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
    sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
    significance <- rbind( significance, sig )
    }
  count <- count + 1
  }
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## Per site results (cont.):  Intracranial volume

`total.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
  {
  if( count >= 8 )
    {
    resultsPerSite <- results[which( results$site == site ),]
    fit <- anova( aov( total.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
    sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
    significance <- rbind( significance, sig )
    }
  count <- count + 1
  }
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

# Results:  Amygdala volume

## All site results:  Amygdala volume (right)

```{r,results = 'asis', echo = T}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
fit <- aov( volume.right.amygdala ~ dx.group + site + age + fiq, data = results )
print( xtable( anova( fit ) ), type = "html" )
```

## Per site results:  Amygdala volume (right)

`volume.right.amygdala ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count < 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( volume.right.amygdala ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## Per site results (cont.):  Amygdala volume (right)

`volume.right.amygdala ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count >= 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( volume.right.amygdala ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## All site results:  Amygdala volume (left)

```{r,results = 'asis', echo = T}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
fit <- aov( volume.left.amygdala ~ dx.group + site + age + fiq, data = results )
print( xtable( anova( fit ) ), type = "html" )
```

## Per site results:  Amygdala volume (left)

`volume.left.amygdala ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count < 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( volume.left.amygdala ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## Per site results (cont.):  Amygdala volume (left)

`volume.left.amygdala ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count >= 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( volume.left.amygdala ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```


# Results:  CSF volume

## All sites:  CSF volume

```{r,results = 'asis', echo = T}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
fit <- aov( csf.volume ~ dx.group + site + age + fiq, data = results )
print( xtable( anova( fit ) ), type = "html" )
```

## Per site results:  CSF volume

`csf.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count < 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( csf.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## Per site results (cont.):  CSF volume

`csf.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count >= 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( csf.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

# Results:  Gray matter volume

## All sites:  Gray matter volume

```{r,results = 'asis', echo = T}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
fit <- aov( gray.matter.volume ~ dx.group + site + age + fiq, data = results )
print( xtable( anova( fit ) ), type = "html" )
```

## Per site results:  Gray matter volume

`gray.matter.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count < 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( gray.matter.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## Per site results (cont.):  Gray matter volume

`gray.matter.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count >= 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( gray.matter.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```


# Results:  White matter volume

## All sites:  White matter volume

```{r,results = 'asis', echo = T}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
fit <- aov( white.matter.volume ~ dx.group + site + age + fiq, data = results )
print( xtable( anova( fit ) ), type = "html" )
```

## Per site results:  White matter volume

`white.matter.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count < 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( white.matter.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## Per site results (cont.):  White matter volume

`white.matter.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count >= 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( white.matter.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```


# Results:  Deep gray matter volume

## All sites:  Deep gray matter volume

```{r,results = 'asis', echo = T}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
fit <- aov( deep.gray.matter.volume ~ dx.group + site + age + fiq, data = results )
print( xtable( anova( fit ) ), type = "html" )
```

## Per site results:  Deep gray matter volume

`deep.gray.matter.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count < 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( deep.gray.matter.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## Per site results (cont.):  Deep gray matter volume

`deep.gray.matter.volume ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count >= 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( deep.gray.matter.volume ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```


# Results:  Total mean thickness

## All sites:  Total mean thickness

```{r,results = 'asis', echo = T}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
fit <- aov( total.mean.thickness ~ dx.group + site + age + fiq, data = results )
print( xtable( anova( fit ) ), type = "html" )
```

## Per site results:  Total mean thickness

`total.mean.thickness ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count < 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( total.mean.thickness ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

## Per site results (cont.):  Total mean thickness

`total.mean.thickness ~ dx.group + age + fiq`

```{r,results = 'asis', echo = F}
library( xtable )
results <- read.csv( './Data/labelresultsAntsSubset.csv' )
significance <- data.frame( site = character(), dx.Pvalue = numeric(),
age.Pvalue = numeric(), fiq.Pvalue = numeric(), stringsAsFactors = TRUE )

count <- 0
for( site in levels( results$site ) )
{
 if( count >= 8 )
 {
  resultsPerSite <- results[which( results$site == site ),]
  fit <- anova( aov( total.mean.thickness ~ dx.group + age + fiq, data = resultsPerSite ) )
  sig <- data.frame( site = site, dx.Pvalue = fit[,5][1], age.Pvalue = fit[,5][2], fiq.Pvalue = fit[,5][3] )
  significance <- rbind( significance, sig )
 }
 count <- count + 1
}
print( xtable( significance ), type = "html", include.rownames = FALSE )
```

# New stuff
